---
title: "Final assignment"
author: "Yi Yen Huang"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r,include = FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(car)
library(haven)
library(psych)
library(tinytex)
library(moments)
library(visdat)
library(dplyr)
library(scales)
```
#Research Question
#what is the relationship between the percentage of teachers’ in-school professional-collaborative-learning and
#the frequency of the implementation of cognitive-activation teaching strategies?

#Data Reading and Data Wrangling
#In this report, I use TALIS 2013 dataset.
#To read the data I used the haven package as follows:
#Reading the PISA2018 dataset
```{r}
df <- read_sas("/Users/elainehuang/Documents/R, personal/ttgallt2.sas7bdat")
```
#Data subsetting
#Now I can start subsetting the relevant questions from the TALIS 2013 questionnaire.
#The relevant variables are:
# - Teaching in General/ How often do you/ collaboration (8 items)
# - Your Teaching/ How often happens/ cognitive teaching (3 items)
# - Relevant demographics (gender, age, current employment status)

#Creating a subset with the variables of interest
```{r}
df1 <- df %>% select(IDCNTRY,IDTEACH, TT2G01,TT2G02, TT2G03, #CountryID, TeacherID, Gender, Age, employment status
                     TT2G33A: TT2G33H, #How often do you collaborate
                     TT2G42A:TT2G42H) #How often do cognitive teaching happens
```
#Saving the dataset to not have it to the big one each time.

#Next I filtered by the countries.
#In this report, I focus on Korea and Denmark.
#After that I re-code their IDs to names.

#Filtering by country
```{r}
df1 <- df %>%
  filter(IDCNTRY == 410 | IDCNTRY == 208)
```
#Recode country IDs to names. Because of conflicts in the recode command between dplyr
#and car package, I specified which to use.
```{r}
df1$IDCNTRY <- df1$IDCNTRY %>%
as.factor %>%
dplyr::recode(`410` = "Korea",
`208` = "Denmark")
```
#Recode the name of the Gender column and the values from 1 to female teacher, and 2 to male teacher

```{r}
df1 <- df1 %>%
  rename(gender = TT2G01)
df1$gender <- df1$gender %>%
  as.factor %>%
  dplyr::recode(`1` = "Female",
                `2` = "Male")
```
#Recode the group name of age.
```{r}
df1 <- df1 %>%
  rename(age = TT2G02)
```
#Recode the name of status of employment column and the values
#1 = Full-time (more than 90% of full-time hours)
#2 = Part-time (71-90% of full-time hours)
#3 = Part-time (50-70% of full-time hours)
#4 = Part-time (less than 50% of full-time hours)
```{r}
df1 <- df1 %>%
  rename(employ_status = TT2G03)
df1$employ_status <- df1$employ_status %>%
  as.factor %>%
  dplyr::recode(`1` = "Full-time (more than 90% of full-time hours)",
                `2` = "71-90% of full-time hours",
                `3` = "50-70% of full-time hours",
                `4` = "less than 50% of full-time hours")
```
#Preparing Variables
#Recode the group name of frequency of teachers collaboration.
#In this variable 1 = never,
#2 = Once a year or less,
#3 = 2-4 times a year,
#4 = 5-10 times a year,
#5 = 1-3 times a month, and
#6 = Once a week or more
```{r}
df1 <- df1 %>%
  rename(collaboration = TT2G33A:TT2G33H)
```
#Recode the group name of frequency of cognitive-activation teaching.
#In this variable 1 = Never or almost never,
#2 = Occasionally,
#3 = Frequently,
#4 = In all or nearly all lessons
```{r}
df1 <- df1 %>%
  rename(cog_active = c(TT2G42B, TT2G42G, TT2G42H))
```
#Recode the NA values to 0, might be missing values
```{r}
df1$collaboration1[is.na(df1$collaboration1)] <- 0
df1$collaboration2[is.na(df1$collaboration2)] <- 0
df1$collaboration3[is.na(df1$collaboration3)] <- 0
df1$collaboration4[is.na(df1$collaboration4)] <- 0
df1$collaboration5[is.na(df1$collaboration5)] <- 0
df1$collaboration6[is.na(df1$collaboration6)] <- 0
df1$collaboration7[is.na(df1$collaboration7)] <- 0
df1$collaboration8[is.na(df1$collaboration8)] <- 0
```
#Recode the NA values to 0, might be missing values
```{r}
df1$cog_active1[is.na(df1$cog_active1)] <- 0
df1$cog_active2[is.na(df1$cog_active2)] <- 0
df1$cog_active3[is.na(df1$cog_active3)] <- 0
```

#Finally, I named the final data set df_final to make it easier to use, and saved it in a CSV file to make it
#easier to reload if needed.
#Saving the data set as the final one:
```{r}
df_final <- df1
write.csv2(df_final, file = "~/Documents/df_final.csv")
```

#Visualizing the data

#How often do teachers collaborate?
#First, I wanted to visualize the frequency of teachers collaboration per country,
#which gives us an overview of trends and skewness of each country’s frequency of collaboration.

#However, result from the factor "collaboration" come with eight questions, the visulization will be more complicated.
#Later on I will test the internal consistency with Cronbach alpha.
#If the Cronbach alpha value is acceptable, then I can use the mean of these eight questions to analysize further.
#But at this moment, I only visulize the first question which is the frequency of teaching jointly.


```{r}
library(ggplot2)
```

```{r}
ggplot(df1, aes( x = collaboration1))+
  facet_wrap(.~IDCNTRY, nrow(2)) +
  geom_bar(position = "dodge", fill=rgb(0.2,0.4,0.6,0.6)) +
  theme_classic() +
  ggtitle("Barplot of Teach jointly as a team in the same class per Country") +
  ylab("count") +
  xlab("Teach jointly as a team in the same class") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```

#The barplot tells us that generally Korean teachers teach jointly less than Danish teachers.
#Danish teachers teach jointly more frequently which is mostly once a week or more.
#Second, I used bar plots to visualize jointly teaching per country per gender, this may show some additional
#differences or interesting information.

```{r}
ggplot(df1, aes(x = collaboration1, fill = gender))+
  facet_wrap(.~IDCNTRY, nrow(2)) +
  geom_bar( position = "dodge") +
  ggtitle("Barplot of Teach jointly as a team in the same class per Country") +
  theme_classic() +
  ylab("Count") +
  xlab("Teach jointly as a team in the same class") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#This barplot shows that, in general, female teachers of both countries jointly teach more often than male teachers.
#We can convince this by looking at means and medians of each country per gender.

```{r}
df1%>%
  group_by(Country = as_factor(IDCNTRY), Gender = as_factor(gender)) %>%
  summarise_at(vars(collaboration1),
               list(Mean = mean, Median = median), na.rm = TRUE)
```
#With the result again shows that female teachers work jointly more often in both two countries.
#These differences are even lager in Denmark,
#where the differences of the mean in Denmark is 0.37 and that in Korea is 0.06.
#Next, we can also visualize them if the data is similarly distributed between countries with a boxplot.
```{r}
ggplot(df1, aes(y = collaboration1, x= IDCNTRY)) +
  geom_boxplot(fill = c("#00AFBB")) +
  theme_classic() +
  ggtitle("Boxplot of teaching jointly per Country") +
  ylab("how often of teaching jointly") +
  xlab("Country") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```

#Here the boxplot shows that Danish teachers teach jointly more often than Korean teachers.
```{r}
ggplot(df1, aes(y = collaboration1, x= gender)) +
  facet_wrap(.~IDCNTRY) +
  geom_boxplot(fill = c("#00AFBB")) +
  theme_classic() +
  ggtitle("Barplot of teaching jointly per Country, per Gender") +
  ylab("how often of teaching jointly") +
  xlab("Gender") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#With the boxpolt, we can see that there is almost no difference between two genders of Korean teachers when it comes to teach jointly.
#For Danish teachers, the dispertion of male teachers seems wider.
#To further visualize how the female and male teachers spread while they teach jointly, we can do
#a conditional probability density plot.
```{r}
ggplot(df1, aes( x = collaboration1, fill = gender)) +
  facet_wrap(.~IDCNTRY) +
  geom_density(adjust = 2.5, position = "fill") +
  scale_fill_manual(values = c("#3ccbf4", "#75aadb")) +
  theme_classic() +
  ggtitle("Conditional Probability Plot of teaching jointly per Country,per Gender") +
  ylab("Probability") +xlab("teaching jointly") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#In both country, higher teaching collaboration comes with female teachers.

#Next, I want to know the condition of jointly teaching by employment status.
```{r}
ggplot(df1, aes( x = collaboration1, fill = employ_status))+
  geom_bar(position = "dodge") +
  ggtitle("Barplot of Teach jointly as a team in the same class by employment status") +
  theme_classic() +
  ylab("Count") +
  xlab("Teach jointly as a team in the same class") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#Compared to part-time employment, It seems that most of teachers in the two countries are full-time employed.
#Yet, it is not clear of the correlation between status of employment  and the frequency of teaching jointly.

#Now let's check the distribution of each country.
```{r}
ggplot(df1, aes( x = collaboration1, fill = employ_status))+
  facet_wrap(.~IDCNTRY, nrow(2)) +
  geom_bar(position = "dodge") +
  ggtitle("Barplot of Teach jointly as a team in the same class per Country by employment status") +
  theme_classic() +
  ylab("Count") +
  xlab("Teach jointly as a team in the same class") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#The barplot shows that the frequency by employment status are very unlikely in the two country.
#The boxplot shows that Korean full-time employed teachers are most probably never teaching jointly.
#For Danish full-time employed teachers are the most possible population to teach jointly once or more per week.

#We can also check the mean and median of each status.
```{r}
df1 %>%
  group_by(Country = as_factor(IDCNTRY), Employment_status =as_factor(employ_status)) %>%
  summarise_at(vars(collaboration1),
               list(Mean = mean, Median = median), na.rm = TRUE)
```
#From this table, it seems generally Danish teachers teach jointly moreo ften than Korean teachers results from the higher mean values.
#Concerned with employment status, the distribution of frequency is more even in Danmark but not so in Korea.
#Moreover, it is interesting that the group of most often teaching jointly is those who work less than 50% full hours, in Korea.
#However, there are also a quite portion of non-ignorable missing values.

```{r}
ggplot(df1, aes(y = collaboration1, x= employ_status)) +
  facet_wrap(.~IDCNTRY) +
  geom_boxplot(fill = c("#00AFBB")) +
  theme_classic() +
  ggtitle("Barplot of teaching jointly per Country, per employ status") +
  ylab("teaching jointly") +
  xlab("employment status") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#The distribution of Korean teachers is quite interesting.
#As a result the further research can dig deeper into Korean teachers independently.
#To further visualize how the employment status populations are distributed between teaching jointly, we can do a conditional probability density plot.
```{r}
ggplot(df1, aes( x = collaboration1, fill = employ_status)) +
  facet_wrap(.~IDCNTRY) +
  geom_density(adjust = 2.5, position = "fill") +
  scale_fill_manual(values = c("#3ccbf4", "#75aadb", "green", "blue")) +
  theme_classic() +
  ggtitle("Conditional Probability Plot of teaching jointly per Country,per employment status") +
  ylab("Probability") +
  xlab("teaching jointly") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#Again, the distribution in Danmark is more evenly.
#In Korea is not even and far from linear association.

#Next I want to visualize the frequency of Students work in small groups to come up with a joint solution to a problem
```{r}
ggplot(df1, aes( x = cog_active1))+
  facet_wrap(.~IDCNTRY, nrow(2)) +
  geom_density(adjust = 3.5, fill="#ff7733") +
  theme_classic() +
  ggtitle("Density Plot of student work jointly per Country") +
  ylab("Population Percentage") +
  xlab("Student work jointly to solve problems") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#Then I want to know more about the differences by gender
```{r}
ggplot(df1, aes( x = cog_active1, fill = gender))+
  facet_wrap(.~IDCNTRY, nrow(2)) +
  geom_density(adjust = 3.5, alpha = .3) +
  theme_classic() +
  ggtitle("Density Plot of student work jointly per Country per gender") +
  ylab("Population Percentage") +
  xlab("Student work jointly to solve problems") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#The density plot show that in Denmark the gender is not so obvious difference.
#In Korea, male teachers seem more possible to never let student work jointly,
#and female teachers show more possibilities to let student work jointly frequently.
#In Denmark, the differences between genders seem to be very small.
#I will calculate the mean, median, and skewness to have more information.

```{r}
df1 %>%
  group_by(Country = as_factor(IDCNTRY), Gender = as_factor(gender)) %>%
  summarise_at(vars(cog_active1),
               list(Mean = mean, Median = median, Skewness = skewness),
               na.rm = TRUE)
```
#The Mean value of Denmark is higher than Koreas, which means Danish students work jointly more often than Korean students.
#To know the different between gender in each country, I am gonna use t-test.
#And beforehand, check the homogeneity of variance by LeveneTest.
```{r}
LeveneTest_cog_active1_country <-leveneTest(cog_active1~as_factor(IDCNTRY), df1)
LeveneTest_cog_active1_country
```
#P=0.232, this case does not meet the homogeneity of variance.
##Unfortunately

```{r}
t.test_cog_active1_country <- t.test(cog_active1~as_factor(IDCNTRY),
                                     data = df1,
                                     alternative = "two.sided",
                                     var.equal = FALSE) # Homogeneity of variance not assumed
t.test_cog_active1_country
```
#mean in group Denmark is 2.462388, mean in group Korea is 1.797136.
#t(6163.7)=25.367, P<.05
#The difference between two countries is significant.
#Overall, the mean value of Denmark is higher than Koreas.
#Nevertheless, to test two countries separately is better to analysis the gender and employment status.
#Finally, I will do a quantile-quantile plot, or Q-Q plot to have a last complementary analyses that will tell
#us how much the data is normally distributed or not.
```{r}
ggplot(df1, aes(sample = cog_active1)) +
  stat_qq() +
  stat_qq_line() +
  theme_classic() +
  ggtitle("Q-Q Plot of students working jointly per country") +
  ylab("Sample Quantiles") +
  xlab("Normal Theoretical Quantiles") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#In this plot we can visualize the skewness analysis that was previously calculated.
#The staircase pattern is present because of the limited amount of values in our sample, which go from 0 to 4 as discrete values. 
#The values that go from y = (0, 2, 3, 4)are mostly on the 45° slope, only the y = 1 deviate from the slope.
#Overall, the data is sightly left skewed.
#The data is not normally distributed.

#Relationship between teachers teaching jointly and students learning jointly
#First, I visualize the relationship between the two variables with a scatter plot and a regression line to
#see if there is a correlation, separating results between genders, as we have seen they have had differences in their results.
```{r}
ggplot(df1, aes(y = cog_active1, x = collaboration1)) +
  facet_wrap(.~IDCNTRY, nrow(2)) +
  geom_jitter(width = 0.1, height = 0.5, alpha = 0.4, size = 0.3, shape =2) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  coord_cartesian(expand = FALSE) +
  ggtitle("Scatter Plot of teaching jointly and learning jointly by country") +
  theme_classic() +
  ylab("students work jointly") +
  xlab("teachers teach jointly") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#It seems that Korean teachers tend to have a positive correlation, where more often teach jointly 
#may come with more often students work jointly as well.
#In Denmark, there is also slightly positive relationship but not that obvious as Korea.
#I’m going to check for gender to see if I can identify any difference.
```{r}
ggplot(df1, aes(y = cog_active1, x = collaboration1, color = gender))+
  facet_wrap(.~IDCNTRY, nrow(2)) +
  geom_jitter(width = 0.1, height = 0.5, alpha = 0.4, size = 0.3, shape =2) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  coord_cartesian(expand = FALSE) +
  theme_classic() +
  ggtitle("Scatter Plot of teaching jointly and learning jointly by country") +
  ylab("students work jointly") +
  xlab("teachers teach jointly") +
  theme(axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))
```
#This scatterplot tells us there are both correlation in Denmark and Korea
#There is also differences between males and females.
#Inferential Data Analysis
#By analyzing a linear regression model to test if there is a relationship between the two variables
```{r}
LM_Test <- lm(cog_active1~collaboration1, df1)
output <- summary(LM_Test)
output
```
#The model suggests there is a relationship between the two variables where, for every additional point in
#teaching jointly, students working jointly increases 0.114493.
#p = .000, reject the null hypothesis.
#Therefore, there is statistic significance  between teaching jointly and student working jointly.

#My research question is
#what is the relationship between the frequency of teachers’ in-school professional-collaborative-learning and the frequency of the implementation of cognitive-activation teaching strategies?

#The frequency of teacher collaboration is measured by means of eight items (e.g., “Teaching in General/ How often do you/ collaboration”) using a 6-point Likert scale (i.e., 1 - never, 6 - Once a week or more). 
#Thus, lower scores in these scales reflect less collaboration, whereas higher scores capture more collaboration.
#I will first assess the internal consistency of the scale by computing cronbach alpha value between the eight items. 
#I can do this by using the alpha() function from the psych package:

```{r}
df_collaboration <- df1 %>% 
  select(collaboration1,collaboration2,collaboration3,collaboration4,collaboration5,collaboration6,collaboration7,collaboration8) %>%as.data.frame() 

psych::alpha(df_collaboration)

```
#A Cronbach’s alpha of 0.87 is quite acceptable.
#Therefore, we could assume that the eight items produce similar scores and that they are a reliable instrument for assessing the same construct.

#Hence, I could compute an average score of attitudes toward school performance (i.e., Collaboration) by #calculating the mean of the eight items. I will use the function rowMeans() to calculate the mean of the
#values of different columns in the dataset.

```{r}
mean_collaboration <- rowMeans(df_collaboration[,1:8],na.rm = TRUE)
```

#Similarly, the frequency of teacher use cognitive-activation strategies is measured by means of three items (e.g., “Your Teaching/ How often happens/ cognitive teaching”) using a 4-point Likert scale (i.e., 1 - Never or almost never, 4 - In all or nearly all lessons). 
```{r}
df_cog_active <- df1 %>% select(cog_active1,cog_active2,cog_active3) %>% 
  as.data.frame() 

psych::alpha(df_cog_active)
```
#A Cronbach’s alpha of 0.87 is quite acceptable.
#Therefore, I could assume that the three items produce similar scores and that they are a reliable instrument for assessing the same construct.
#Hence, I could compute an average score of attitudes toward school performance (i.e., Collaboration) by #calculating the mean of the eight items. I will use the function rowMeans() to calculate the mean of the
#values of different columns in the dataset.


```{r}
mean_cog_active <- rowMeans(df_cog_active[,1:3])
```

#I have examed the internal consistency of collaboration and cognitive-activation so now I can check if there is the linear correlation between each other.
```{r}
LM_Test_group <- lm(mean_cog_active~mean_collaboration, df1)
output <- summary(LM_Test_group)
output
```
#The model suggests that there is a statistically significant positive relationship between the frequency of teacher collaboration and the implement  frequency of cognitive-activation (b = 1.06, t(8182) = 33.61, p < .001. This is, the more often the teachers collaborate, the higher frequency that they teach with cognitive-activation strategies.

#Conclusion
#I am very glad that I can use R to find some clues to myresearch questions! Pretty enjoy it.
#Next, I would love to learn about SEM.
#I believev it will be fun!

